### 2016-10-04 Paper_v7.tex
Small changes

The predictive power of the ensemble was tested using both cross validation and by comparing simulations with data sets not used for model training.
In whole, 100\% of our training objectives were statistically significant (at a 95\% confidence interval) compared to a randomized parameter family (N = 100)
generated from a random starting point. Conversely, we \emph{predicted} 100\% of the training objectives, at a 95\% confidence interval compared to randomized parameters (Wicoxon non-parametric test).
The model also captured the temporal gene expression responses of E-cadherin, pSmad2, and LEF-1 (not used for model training) to within one-standard deviation (up to the 48 hr time-point) (Fig. \ref{fg:F2}J-L). Taken together, the model captured the key signaling events revealed by Medici \emph{et al.} \citep{Medici:2008fk} that drive the phenotypic conversion.
A listing of objective function values resulting from training, cross validation and the random parameter control is given in the supplement (Fig. \ref{fg:ObjTable}).

>>>>

The predictive power of the ensemble was tested using both cross validation and by comparing simulations with data sets not used for model training.
In whole, all of our training objectives were statistically significant (at a 95\% confidence interval) compared to a randomized parameter family (N = 100)
generated from a random starting point. Conversely, we \emph{predicted} all of the training objectives, at a 95\% confidence interval compared to randomized parameters (Wicoxon non-parametric test). The model also captured the temporal gene expression responses of E-cadherin, pSmad2, and LEF-1 (not used for model training) to within one-standard deviation (up to the 48 hr time-point) (Fig. \ref{fg:F2}J-L). Taken together, the model captured the key signaling events revealed by Medici \emph{et al.} \citep{Medici:2008fk} that drive the phenotypic conversion.
A listing of objective function values resulting from training, cross validation and the random parameter control is given in the supplement (Fig. \ref{fg:ObjTable}).
